\textbf{First Class scholarship for comprehensive excellence} \hfill Oct. 2023 \\
{\small Tsinghua University\hfill  Beijing, China}

\vspace{4pt}

\textbf{Excellent Team for Big Data Practice Course Project} \hfill Nov. 2022 \\
{\small Awarded for research: ``Bioinformatics Research on Childhood Hearing Loss'', Tsinghua University \hfill Beijing, China}

\vspace{4pt}

\textbf{Outstanding Oral Report Award} \hfill Sept. 2022 \\
{\small Presented at the 8$^{th}$ Academic Forum on Molecular Biochemistry, Peking University \hfill Beijing, China}

\vspace{4pt}

\textbf{Second Class scholarship for comprehensive excellence} \hfill Nov. 2021 \\
{\small Tsinghua University \hfill Beijing, China}

\vspace{4pt}

\textbf{Star of Graduate Students} \hfill Dec. 2020 \\
{\small Top student from each college, Tsinghua University \hfill Beijing, China}

\vspace{4pt}

\textbf{``Hundred'' Outstanding Undergraduate Theses} \hfill Jun. 2019 \\
{\small Top student from each college, Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Outstanding Undergraduate Thesis at the University Level} \hfill May. 2019 \\
{\small Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Top Ten Excellent Graduate in Scientific Research} \hfill May. 2019 \\
{\small College of Veterinary Medicine, Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Boehringer-Ingelheim Scholarship} \hfill Oct. 2019 \\
{\small Boehringer-Ingelheim \hfill Shaanxi, China}
    
\vspace{4pt}

\textbf{Silver Prize for National-Level Undergraduate Research Training Program} \hfill 2018 \\
{\small China Agricultural University \hfill Beijing, China}

\vspace{4pt}

\textbf{Golden Prize for University-Level Undergraduate Entrepreneurship Training Program} \hfill Jun. 2017 \\
{\small Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Silver Prize for the ``Challenge Cup'' Entrepreneurship Plan Competition} \hfill 2016 \\
{\small Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Second Prize for Chemical Experiment Skills Competition} \hfill 2016 \\
{\small Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Silver Prize for the ``Internet+'' Innovation and Entrepreneurship Competition (Shaanxi)} \hfill Sept. 2016 \\
{\small Win honors for Northwest A\&F University, ``Internet+'' Shaanxi Organizing Committee \hfill Shaanxi, China}

\vspace{4pt}

\textbf{National Scholarship} \hfill 2015 $\sim$ 2016 \\
{\small The Highest Level of Award for Undergraduate. 2015,2016, two-time winner. \hfill Ministry of Education of P. R. China}\\


\vspace{4pt}

\textbf{First-Class Scholarship for Professional Excellence} \hfill 2015 $\sim$ 2019 \\
{\small 2015,2016,2017,2018,2019, five-time winner, Northwest A\&F University \hfill Shaanxi, China}

\vspace{4pt}

\textbf{Merit Student} \hfill 2015 $\sim$ 2019 \\
{\small 2015,2016,2017,2018,2019, five-time winner, Northwest A\&F University \hfill Shaanxi, China}
