\begin{enumerate}
    \item \textbf{Bioinformatics}
    \begin{itemize}
        \item Specialized in omics analysis using high-throughput sequencing data.
        \item Proficient in handling sequencing data from RNA-seq, Hi-C, ATAC-seq, ChIP-seq, Ribo-seq, etc.
        \item Deep understanding and practical experience with \href{https://yilab.org.cn/}{Yilab}'s \href{https://www.nature.com/articles/s41586-022-04836-5}{Detect-seq and Targeted deep Sequencing} technologies.
        \item Skilled in using protein amino acid sequence structure prediction tools: AlphaFold2/3, Colabfold, ESMFold, etc.
        \item Skilled in using sequence and structure search tools: BLAST kits, MMSeqs2, Foldseek, Dali, etc.
    \end{itemize}
    \item \textbf{Development Skills}
    \begin{itemize}
        \item Seasoned Python developer and instructor with expertise in developing 
        command-line tools, Python libraries/packages, websites, web scrapers, etc.
        \item Proficient in Python/R data analysis, visualization, and implementation of basic machine learning methodologies.
        \item Experienced in Shell scripting, including Bash, Zsh, and PowerShell.
        \item Experienced in working with Linux/MacOS/Windows platforms and task management systems like SLURM.
        \item Skilled in using Git/GitHub, Docker, conda, and poetry framework for code management, environment management, and Python development.
        \item Familiarity with a wide range of Python packages: pandas, numpy, Matplotlib, Seaborn, pysam, biopython, polars, sci-kit learn, pytorch, etc.
        \item Experienced in using \LaTeX.
    \end{itemize}
    \item \textbf{Wet Experiment Skills}
    \begin{itemize}
        \item Possess anatomical experience with fish, poultry, rabbits, pigs, dogs, frogs, and mice.
        Experienced in performing cat desexing surgeries.
        Skilled in blood sampling and injection techniques for rabbits, rats, and mice.
        Holds a B.V.Sc degree and possesses rich experience in animal experiment trainning.
        \item Experienced in molecular cloning experiments, including primer design, DNA/RNA extraction, PCR, and gel electrophoresis.
        \item Experienced in bacteria experiments, including bacteria culture, transformation, and plasmid amplification.
        \item Experienced in mammalian cell experiments, including cell culture, transfection, western blot, and immunofluorescence staining.
    \end{itemize}
    \item \textbf{Problem Solving and Leadership}
    \begin{itemize}
        \item Proven ability to solve complex problems in bioinformatics and software development.
        \item Strong leadership skills with experience in guiding and mentoring teams in project management and delivering successful outcomes.
        \item Effective communicator with the ability to collaborate across disciplines and drive projects forward.
    \end{itemize}
\end{enumerate}


