\textit{The following individuals are able to provide me with reference letters upon your request.}

\subsubsection*{\href{https://www.bio.pku.edu.cn/enhomes/news/teacher_dis/91.html}{Dr. Chengqi Yi}}
Advisor\\
School of Life Sciences, Peking University, Beijing, China\\
\href{mailto:chengqi.yi@pku.edu.cn}{chengqi.yi@pku.edu.cn}\\

\subsubsection*{\href{https://profiles.ucalgary.ca/herman-barkema}{Dr. Herman Barkema}}
Mentor\\
Faculty of Veterinary Medicine, University of Calgary, Calgary, AB, Canada\\
\href{mailto:barkema@ucalgary.ca}{barkema@ucalgary.ca}\\

\subsubsection*{\href{https://life.tsinghua.edu.cn/lifeen/info/1034/1077.htm}{Dr. Wei Xie}}
Rotating Advisor\\
School of Life Sciences, Tsinghua University, Beijing, China\\
\href{mailto:xiewei121@tsinghua.edu.cn}{xiewei121@tsinghua.edu.cn}\\



\subsubsection*{\href{https://life.tsinghua.edu.cn/lifeen/info/1034/1083.htm}{Dr. Zhi John Lu}}
Rotating Advisor\\
School of Life Sciences, Tsinghua University, Beijing, China\\
\href{mailto:zhilu@tsinghua.edu.cn}{zhilu@tsinghua.edu.cn}\\


\subsubsection*{\href{https://faculty.nwu.edu.cn/gaomingqing/zh_CN/index.htm}{Dr. Mingqing Gao}}
Advisor\\
School of Medicine, Northwest University, Shaanxi, China\\
\href{mailto:gaomingqing@nwu.edu.cn}{gaomingqing@nwu.edu.cn}\\



\subsubsection*{\href{https://cvm.cau.edu.cn/art/2017/9/12/art_41957_71.html}{Dr. Jian Gao}}
Advisor\\
College of Veterinary Medicine, China Agricultural University, Beijing, China\\
\href{mailto:gaojian2016@cau.edu.cn}{gaojian2016@cau.edu.cn}\\


\subsubsection*{\href{https://dyxy.nwsuaf.edu.cn/en/People/FullProfessor/5e6012bf013a499c946289472b285795.htm}{Dr. Qin Zhao}}
Advisor\\
College of Veterinary Medicine, Northwest A\&F University, Shaanxi, China\\
\href{mailto:qinzhao\_2004@nwafu.edu.cn}{qinzhao\_2004@nwafu.edu.cn}\\
