\subsection*{\textbf{Selected Open Source Softwares that I developed}}
\begin{itemize}
    \item \href{https://github.com/hermanzhaozzzz/bioat}{bioat}: A Python package \& a command line toolkit for Bioinformatics and data science. (\href{https://pypi.org/project/bioat/}{PyPi} | \href{https://github.com/hermanzhaozzzz/bioat}{GitHub}).
    \item \href{https://github.com/hermanzhaozzzz/.my_shell_envs}{.my\_shell\_envs}: A fast deployment tool for shell (zsh) envs.
    \item \href{https://github.com/hermanzhaozzzz/My-Opencore-EFI-for-AMD3900X-5700XT-TUF-x570-Hackintosh}{My-Opencore-EFI-for-Hackintosh}: A project to help a personal computer run the macOS system.
\end{itemize}

\subsection*{\textbf{Selected Open Source Bioinformatic Analysis Tools that I developed}}
\begin{itemize}
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_RNA-seq}{snakepipes\_RNA-seq}: A ``Snakemake'' pipeline for RNA-seq data analysis.
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_Hi-C}{snakepipes\_Hi-C}: A ``Snakemake'' pipeline for Hi-C data analysis.
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_ATAC-seq}{snakepipes\_ATAC-seq}: A ``Snakemake'' pipeline for ATAC-seq data analysis.
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_ChIP-seq}{snakepipes\_ChIP-seq}: A ``Snakemake'' pipeline for ChIP-seq data analysis.
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_detect-seq}{snakepipes\_detect-seq}: A ``Snakemake'' pipeline for detect-seq data analysis.
    \item \href{https://github.com/hermanzhaozzzz/snakepipes_fastqc-multiqc}{snakepipes\_fastqc-multiqc}: A ``Snakemake'' pipeline for quality control of NGS/HTS data.
\end{itemize}

\subsection*{\textbf{Selected Open Source Softwares/Tools that I contribute codes or issues}}
\begin{itemize}
    \item \href{https://github.com/owkin/PyDESeq2}{PyDESeq2}: PyDESeq2 is a Python implementation of the DESeq2 method for differential 
    expression analysis (DEA) with bulk RNA-seq data, originally in R.
    \item \href{https://github.com/DessimozLab/fold_tree}{fold\_tree}: This repo contains the scripts and snakemake workflow for making and benchmarking structure based trees using Foldseek.
    \item \href{https://github.com/python-poetry/poetry}{poetry}: Poetry is a tool for dependency management and packaging in Python.
\end{itemize}
